\chapter{OVERVIEW ABOUT PROJECT}

\renewcommand{\headrulewidth}{0.5pt}
\renewcommand{\footrulewidth}{0.5pt}
\thispagestyle{plain}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\textbf{CHAPTER 1}}
\fancyhead[R]{\textbf{Graduate Report}}
\raggedright
\fancyfoot[L]{From: Nguyen Van Anh Tuan}
\fancyfoot[R]{Page \thepage}

\section{Reasons For Choosing The Topic}
    During the time of entering the internship unit, after being briefly introduced to the systems, components and equipment 
    at BAA Training Vietnam, accompanied by the instructor's suggestion, I realized the importance of the system. The importance 
    of applying flight simulators in pilot training. \\ 
    \vspace{3mm}
    But because the practice process is not too long to understand all the functions of the device. Since then, I have chosen the 
    topic of learning about the maintenance process of the flight simulator and the components related to the flight simulator for 
    this graduation internship.

\section{The Target of Research}
    Through the implementation of this topic, I personally want to have more understanding about the maintenance process of a flight 
    simulator, what is the MPIC system, and at the same time experience a working environment. Dynamic, open-minded, absorbing practical 
    knowledge. Thereby cultivating yourself and adding other necessary skills in the working process.

\section{Research Methods}
    The study uses the method of collecting secondary data from reputable books, websites and internal information of BAA Training Vietnam 
    company. In addition, the primary data collection method was also used through observation and recording during the internship.

\section{Research Scope}
    \subsection{In Term of Time}
        From March 1st 2021 to June 1st 2021
    \subsection{In Term of Space}
        At BAA Training Vietnam company