\chapter{BIBLIOGRAPHY}

\renewcommand{\headrulewidth}{0.5pt}
\renewcommand{\footrulewidth}{0.5pt}
\thispagestyle{plain}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\textbf{CHAPTER 6}}
\fancyhead[R]{\textbf{Intelligent Traffic System}}
\raggedright
\fancyfoot[L]{From: ITM Vision}
\fancyfoot[R]{Page \thepage}

\begin{enumerate}
    \item NVIDIA blog, \url{https://blogs.nvidia.com/} .
    \item M. Coşkun , Ö. Yıldırım , A. Uçar and Y. Demır , "AN OVERVIEW OF POPULAR DEEP LEARNING METHODS", European Journal of Technique (EJT), vol. 7, no. 2, pp. 165-176, Dec. 2017.
    \item Z. Zhao, P. Zheng, S. Xu and X. Wu, "Object Detection With Deep Learning: A Review," in IEEE Transactions on Neural Networks and Learning Systems, vol. 30, no. 11, pp. 3212-3232, Nov. 2019.
    \item Adrian Rosebrock, Intersection over Union (IoU) for object detection, PyImageSearch, \url{https://www.pyimagesearch.com/2016/11/07/intersection-over-union-iou-for-object-detection/}, accessed on 01 March 2021.
    \item Ignacio Icke. Overfitting. [Online; accessed May 24, 2017]. 2008. URL: \url{https://en.wikipedia.org/wiki/Overfitting#/media/File:Overfitting}.
    \item Deepa, R.Tamilselvan, E.Abrar, E.Sampath, S. (2019). Comparison of Yolo, SSD, Faster RCNN for Real Time Tennis Ball Tracking for Action Decision Networks. 2019 International Conference on Advances in Computing and Communication Engineering (ICACCE).
    \item J. -a. Kim, J. -Y. Sung and S. -h. Park, "Comparison of Faster-RCNN, YOLO, and SSD for Real-Time Vehicle Type Recognition," 2020 IEEE International Conference on Consumer Electronics - Asia (ICCE-Asia), Seoul, Korea (South), 2020, pp. 1-4.
    \item . Redmon et al. “You Only Look Once: Unified, Real-Time Object Detection”. In: 2016 IEEE Conference on Computer Vision and Pattern Recognition (CVPR) 2016, pp. 779–788.
    \item J. Redmon and A. Farhadi, “Yolov3: An incremental improvement,” CoRR, vol. abs/1804.02767, 2018.
    \item Bochkovskiy, A., Wang, C. Y., Liao, H. Y. M., 2020. YOLOv4: Optimal Speed and Accuracy of Object Detection.
    \item Ethan Yanjia Li, Dive Really Deep into YOLO v3: A Beginner’s Guide, \url{https://towardsdatascience.com/dive-really-deep-into-yolo-v3-a-beginners-guide-9e3d2666280e}.
    \item Liu W. et al. (2016) SSD: Single Shot MultiBox Detector. In: Leibe B., Matas J., Sebe N., Welling M. (eds) Computer Vision – ECCV 2016. ECCV 2016. Lecture Notes in Computer Science, vol 9905. Springer, Cham. \url{https://doi.org/10.1007/978-3-319-46448-0_2}.
    \item Shaoqing Ren, Kaiming He, Ross Girshick, and Jian Sun. Faster r-cnn: Towards realtime object detection with region proposal networks. In Advances in neural information processing systems, pages 91–99, 2015.
    \item Z. Chen, R. Khemmar, B. Decoux, A. Atahouet, and J. Ertaud. Real time object detection, tracking, and distance and motion estimation based on deep learning: Application to smart mobility. In 2019 Eighth International Conference on Emerging Security Technologies (EST), pages 1–6, 2019.
    \item Mahto, Pooja and Garg, Priyamm and Seth, Pranav and Panda, J, Refining Yolov4 for Vehicle Detection (June 16, 2020). International Journal of Advanced Research in Engineering and Technology (IJARET), 11(5), 2020, pp. 409-419.
    \item Luo, W., Xing, J., Milan, A., Zhang, X., Liu, W., \& Kim, T. K. (2020). Multiple object tracking: A literature review. Artificial Intelligence, 103448.
    \item Bewley, A.; Ge, Z.; Ott, L.; Ramos, F.; Upcroft, B. Simple online and realtime tracking. In Proceedings of the 2016 IEEE International Conference on Image Processing (ICIP), Phoenix, AZ, USA, 25–28 September 2016; pp. 3464–3468.
    \item Wojke, N.; Bewley, A.; Paulus, D. Simple online and realtime tracking with a deep association metric. In Proceedings of the 2017 IEEE International Conference on Image Processing (ICIP), Beijing, China, 17–20 September 2017; pp. 3645–3649.
    \item Nayak, R., Behera, M. M., Pati, U. C., \& Das, S. K. (2019). Video-based Real-time Intrusion Detection System using Deep-Learning for Smart City Applications. 2019 IEEE International Conference on Advanced Networks and Telecommunications Systems (ANTS).
    \item Chen, C., Liu, B., Wan, S., Qiao, P., \& Pei, Q. (2020). An Edge Traffic Flow Detection Scheme Based on Deep Learning in an Intelligent Transportation System. IEEE Transactions on Intelligent Transportation Systems, 1–13.
    \item Mittal, Sparsh. "A Survey on optimized implementation of deep learning models on the NVIDIA Jetson platform." Journal of Systems Architecture 97 (2019): 428-442.
    \item K. Bernardin and R. Stiefelhagen, “Evaluating Multiple Object Tracking Performance: The CLEAR MOT Metrics,” Journal on Image and Video Processing, 2008.
    \item Weng, X., Wang, J., Held, D., \& Kitani, K. (2020). 3d multi-object tracking: A baseline and new evaluation metrics. arXiv preprint arXiv:1907.03961.
    \item Zhang, Y., Wang, C., Wang, X., Zeng, W., \& Liu, W. (2020). FairMOT: On the fairness of detection and re-identification in multiple object tracking. arXiv e-prints, arXiv-2004.
    \item Hou, X., Wang, Y., \& Chau, L.-P. (2019). Vehicle Tracking Using Deep SORT with Low Confidence Track Filtering. 2019 16th IEEE International Conference on Advanced Video and Signal Based Surveillance (AVSS).
    \item Paul Heckbert, Fundamentals of Texture Mapping and Image Warping, Master’s thesis, UCB/CSD 89/516, CS Division, U.C. Berkeley, June 1989, \url{http://www.cs.cmu.edu/˜ph}, pages 17-21.
    \item Amrit Krishnan, Jonathan Larsson, Vehicle Detection and Road Scene Segmentation using Deep Learning, Master’s thesis in Complex Adaptive Systems, Department of Signals and Systems, Chalmers University of Technology, Sweeden, 2016, pages 6 - 14.
    \item Erik Bohnsack, Adam Lilja, Multi-Object Tracking using either Endto-End Deep Learning or PMBM filtering, Master’s thesis in Systems, Control and Mechatronics, Department of Electrical Engineering, Chalmers University of Technology, Sweeden, 2019, page 36.
    \item Joachim Benjaminsson, Emil Rosenberg, Multiple Object Tracking with Camera Data and Deep Learning Detectors, Master’s thesis in Communication Engineering, Department of Electrical Engineering, Chalmers University of Technology, Sweeden, 2017, pages 19 - 24.
    \item M. S. Grewal and dawsonera (e-book collection), Kalman filtering: theory and practice using MATLAB, English, 3rd. Oxford: Wiley-Blackwell, 2008.
    \item Hungarian algorithm, May 2017. [Online]. Available: \url{https://en.wikipedia.org/wiki/Hungarian_algorithm}.
\end{enumerate}