\chapter{CONCLUSION}

\renewcommand{\headrulewidth}{0.5pt}
\renewcommand{\footrulewidth}{0.5pt}
\thispagestyle{plain}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\textbf{CHAPTER 5}}
\fancyhead[R]{\textbf{Graduate Report}}
\raggedright
\fancyfoot[L]{From: Nguyen Van Anh Tuan}
\fancyfoot[R]{Page \thepage}

\section{Results}
    During my internship period at BAA Training Vietnam from January 18th 2021 to March 18th 2021, I have learned 
    a lot from working evironment here. \\
    \vspace{3mm}
    Through the documents I have read as well as seen the maintenance process of the flight simulator, I personally 
    see that the working process is not like what I had imagined. It will be quite simple because the equipment 
    provided by the manufacturer to the company does not have too many technical documents as well as machine details 
    inside, so the maintenance work of the maintenance staff here is Start the device, check all panels, as well as 
    lights or buttons, if there is any damage or problem, the technician will review and replace the part, not repair it. \\ 
    \vspace{3mm}
    In addition to the knowledge about pilot training, under the dedicated guidance of the brothers and sisters in the 
    company, I personally also learned more soft skills for the job such as:
    \begin{itemize}
        \item Communication skills when exchanging work with people in the company;
        \item Skills to read and filter documents on topics that you need to care about and research;
        \item Skills when working in a company with a large-scale and professional working model;
        \item Practice self-discipline and be careful when working;
    \end{itemize}

\section{Things That Have Not Been Done}
    Because of the short internship period, only 2 months, I did not understand all aspects of the training programs 
    and did not have much access to the flight simulator at the company. The content shown in this report is the knowledge 
    I have experienced in practice and only stops at the point of view of an intern who can only access everything through 
    references that the technical department at the company provided. \\ 
    \vspace{3mm}
    In addition, at BAA Training Vietnam, contact with foreigners takes place regularly, so English is used frequently to 
    communicate with superiors, colleagues and customers. This was a hindrance for me when I first started my internship, 
    I have never worked in such an environment before so I had some difficulties in communication.

\section{Lessons Learned}
    After completing my internship at BAA Training Vietnam, I realize that I have to study more. The knowledge at the school 
    as a foundation helps me have an overview of the profession I am studying as well as gradually forming a career direction 
    in the future. However, in order to develop myself in the most comprehensive way, I need to learn more, especially soft 
    skills such as how to behave, communicate, connect with people in the company, how to receive information and handle them 
    or work flexibly, etc. They help me work more efficiently, bring more productivity, no longer be surprised when receiving 
    tasks and know how to collect information from many different sources to complete tasks into them. Also an advantage for 
    my upcoming full-time job. However, not to stop learning, cultivating and upgrading from hard skills to soft skills every 
    day is necessary to develop their abilities and knowledge.