\chapter{CONCLUSIONS}

\renewcommand{\headrulewidth}{0.5pt}
\renewcommand{\footrulewidth}{0.5pt}
\thispagestyle{plain}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\textbf{CHAPTER 4}}
\fancyhead[R]{\textbf{DANGEGOUS WEAPONS DETECTION USING YOLOv9}}
\raggedright
\fancyfoot[L]{From: Nguyen Van Anh Tuan}
\fancyfoot[R]{Page \thepage}

\justifying

\section{Conclusions}
    In conclusion, the application of YOLOv9 for dangerous weapon detection represents a significant advancement in the field of computer vision and security. YOLOv9's improved accuracy, speed, and robustness make it an ideal solution for real-time weapon detection in various environments such as airports, schools, and public events. The enhanced capabilities of YOLOv9, including better handling of small and overlapping objects, ensure a higher detection rate, thereby increasing the reliability of security systems. By leveraging the latest advancements in deep learning and object detection, YOLOv9 not only enhances the safety of public spaces but also streamlines the process of identifying potential threats, making it an indispensable tool in modern security protocols. As the technology continues to evolve, further integration of YOLOv9 with other security measures will undoubtedly lead to even more effective and comprehensive safety solutions.
\section{Limitations}
    During process of working and implementing with this project, it will be inevitable that there will be some new knowledge and result or experience that i can see from this project. \\
    \vspace{3mm}
    So, in below here, there will be some advantages and disadvantages in this project that i would like to summary. Balancing these advantages and disadvantages is crucial for effective implementation of YOLOv9 in dangerous weapon detection, ensuring that security measures are both efficient and ethical.
    \subsection{Advantages}
        \begin{itemize}
            \item \textbf{High Accuracy:} YOLOv9 offers enhanced accuracy in detecting various types of weapons, reducing false positives and negatives, and ensuring reliable threat identification.
            \item \textbf{Real-time Detection:} The optimized speed of YOLOv9 allows for real-time detection of weapons, which is crucial for timely interventions in security-sensitive environments.
            \item \textbf{Improved Object Handling:} YOLOv9's advanced architecture can better handle small, overlapping, and partially obscured objects, making it more effective in diverse and complex scenarios.
            \item \textbf{Scalability:} YOLOv9 is designed to be scalable and can be deployed on a range of devices from high-end servers to edge devices, making it versatile for various deployment needs.
            \item \textbf{Robustness:} Enhanced generalization capabilities mean YOLOv9 performs well across different datasets and environments, ensuring consistent performance in real-world applications.
            \item \textbf{State-of-the-Art Techniques:} Incorporating the latest advancements in deep learning, YOLOv9 ensures that security systems benefit from cutting-edge technology, providing a future-proof solution.
            \item \textbf{Active Community Support:} Being the latest version, YOLOv9 has robust community support, frequent updates, and comprehensive documentation, facilitating easier implementation and troubleshooting.
        \end{itemize}
    \subsection{Disadvantages}
        \begin{itemize}
            \item \textbf{High Computational Demand:} Despite optimizations, YOLOv9 can still be computationally intensive, requiring powerful hardware for real-time processing, which might not be feasible for all organizations.
            \item \textbf{Complexity in Implementation:} Integrating YOLOv9 into existing security systems may require significant technical expertise and resources, posing a challenge for organizations with limited technical staff.
            \item \textbf{Training Data Requirements:} Achieving high accuracy with YOLOv9 may necessitate large and diverse training datasets, which can be time-consuming and costly to compile and annotate.
            \item \textbf{Potential Privacy Concerns:} Deploying weapon detection systems in public spaces raises privacy concerns, as constant surveillance can be perceived as intrusive, necessitating careful consideration of ethical implications.
            \item \textbf{False Positives and Negatives:} While YOLOv9 improves detection accuracy, no system is flawless. False positives can lead to unnecessary panic and false negatives can pose serious security risks, necessitating human oversight.
            \item \textbf{Maintenance and Updates:} Regular maintenance and updates are required to keep the detection system effective against new types of weapons and evolving threats, which can be resource-intensive.
            \item \textbf{Dependence on Environmental Conditions:} The performance of YOLOv9 can be affected by environmental conditions such as lighting, weather, and camera quality, potentially impacting its effectiveness in certain scenarios.
        \end{itemize}